### 2020-09-17 priority-gv.tex
Reorganised paper.

\subsubsection{Syntactic Sugar}%
\label{sec:pgv-syntax-sugar}
We define the type of pure functions, \ie functions which perform no communication, and types for internal and external choice. Furthermore, we define term constructs for sequential composition, let-binding, various pattern matching lambda abstractions, fork, which combines channel creation and thread spawning in one construct, and internal and external choice.
\[
\begin{array}{lcl}
  \ty{\tylolli{T}{U}}
  & \elabarrow & \ty{\tylolli[\cs{\ptop},\cs{\pbot}]{T}{U}} \\
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}} \\
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
  \\
  \tm{\andthen{M}{N}}
  & \elabarrow & \tm{\letunit{M}{N}} \\
  \tm{\letbind{x}{M}{N}}
  & \elabarrow & \tm{(\lambda x.N)\;M} \\
  \tm{\lambda\unit.M}
  & \elabarrow & \tm{\lambda z.\letunit{z}{M}} \\
  \tm{\lambda\pair{x}{y}.M}
  & \elabarrow & \tm{\lambda z.\letpair{x}{y}{z}{M}} \\
  \tm{\fork}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\spawn\;{(\lambda\unit.x\;y)}}{z}}} \\
  \tm{\select{\ell}}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\close\;(\send\;{\pair{\ell\;y}{x}})}{z}}} \\
  \multicolumn{3}{l}{\tm{\offer{L}{x}{M}{y}{N}}\elabarrow} \\
  \multicolumn{3}{l}{
  \qquad\tm{\letpair{z}{w}{\recv\;{L}}{\andthen{\wait\;{w}}{\casesum{z}{x}{M}{y}{N}}}}} \\
  \tm{\offeremp{L}}
  & \elabarrow & \tm{\letpair{z}{w}{\recv\;L}{\andthen{\wait\;{w}}{\absurd{z}}}}
\end{array}
\]

>>>>

\subsubsection{Syntactic Sugar}%
\label{sec:pgv-syntax-sugar}

\[
\begin{array}{lcl}
  \ty{\tylolli{T}{U}}
  & \elabarrow & \ty{\tylolli[\cs{\ptop},\cs{\pbot}]{T}{U}} \\
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}} \\
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
  \\
  \tm{\andthen{M}{N}}
  & \elabarrow & \tm{\letunit{M}{N}} \\
  \tm{\letbind{x}{M}{N}}
  & \elabarrow & \tm{(\lambda x.N)\;M} \\
  \tm{\lambda\unit.M}
  & \elabarrow & \tm{\lambda z.\letunit{z}{M}} \\
  \tm{\lambda\pair{x}{y}.M}
  & \elabarrow & \tm{\lambda z.\letpair{x}{y}{z}{M}} \\
  \tm{\fork}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\spawn\;{(\lambda\unit.x\;y)}}{z}}} \\
  \tm{\select{\ell}}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\close\;(\send\;{\pair{\ell\;y}{x}})}{z}}} \\
  \multicolumn{3}{l}{\tm{\offer{L}{x}{M}{y}{N}}\elabarrow} \\
  \multicolumn{3}{l}{
  \qquad\tm{\letpair{z}{w}{\recv\;{L}}{\andthen{\wait\;{w}}{\casesum{z}{x}{M}{y}{N}}}}} \\
  \tm{\offeremp{L}}
  & \elabarrow & \tm{\letpair{z}{w}{\recv\;L}{\andthen{\wait\;{w}}{\absurd{z}}}}
\end{array}
\]
